Open-Set Domain Adaptation through Self-Supervision

### 2022-02-12 paper/main.tex
Results table

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{caption}
% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}
\usepackage{multirow}

@@

As we have already seen in section \ref{sec:method}, the network is composed of a feature extractor $E$, and two heads, $C_{1/2}$ and $R_{1/2}$.
For the feature extraction, we employ a ResNet-18\cite{ResNet18} pre-trained on ImageNet.
All the experiments are run training with a batch size equals to 32 and using a stochastic gradient descent optimization strategy
with a weight decay of 0.0005 and a momentum of 0.9.
The learning rate is set to 0.001 in the cases where we use a single-head rotation classifier as $R_1$, and 0.003 in the multi-head case.
The reason of this choice lies on the fact that, with a multi-head rotation classifier, we have to train 45 heads instead of a single one,
so the training process needs to be speeded up.
Moreover, we set a learning rate 10 times lower for the feature extractor weights.
We also decrease the learning rate using a step learning rate scheduler, which reduces it by a factor of 10 after 90\% of total epochs.
All models are trained for 50 epochs for the step one and for 25 epochs for the step two.
For models using the center loss a centroid learning rate of 0.001 is used.
The other hyperparameters are analyzed performing an ablation on section {\bf INSERT REF}.

@@

\subsection{Results}
\label{sec:results}
\begin{figure*}[h!]
  \centering
  \begin{subfigure}[b]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a1.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a2.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-l.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-th.png}
  \end{subfigure}
  \caption{\label{figurelabel} Test Caption}
\end{figure*}

@@

The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
A few critical points still remain on our method of study and proposed solution.
The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
\newpage
\appendix
\section{Test}

@@

\begin{table}
  \centering
  \begin{tabular}[t]{||c|c|c||c|c||}
    \hline
    \multicolumn{5}{||c||}{Single-Head, CE Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS* \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Multi-Head, CE Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS* \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Single-Head, CE+C Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS* \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Multi-Head, CE+C Loss} \\
    \hline
    Source & Target & AUROC & HOS & HOS* \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline 
    \hline
    \multicolumn{5}{||c||}{No Rotation} \\
    \hline
    Source & Target & AUROC & HOS & HOS$_{Best}$ \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    S & T & 50\% & 30\% & 30\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:results}Results for domain alignment. AUROC is the area under the ROC. HOS is latest achieved HOS, HOS* the best achieved through all epochs.}
\end{table}

>>>>

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{caption}
% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}
\usepackage{multirow}
\usepackage{float}

@@

As we have already seen in section \ref{sec:method}, the network is composed of a feature extractor $E$, and two heads, $C_{1/2}$ and $R_{1/2}$.
For the feature extraction, we employ a ResNet-18\cite{ResNet18} pre-trained on ImageNet.
All the experiments are run training with a batch size equals to 32 and using a stochastic gradient descent optimization strategy
with a weight decay of 0.0005 and a momentum of 0.9.
The learning rate is set to 0.001 in the cases where we use a single-head rotation classifier as $R_1$, and 0.003 in the multi-head case.
The reason of this choice lies on the fact that, with a multi-head rotation classifier, we have to train 45 heads instead of a single one,
so the training process needs to be speeded up.
Moreover, we set a learning rate 10 times lower for the feature extractor weights.
We also decrease the learning rate using a step learning rate scheduler, which reduces it by a factor of 10 after 90\% of total epochs.
All models are trained for 50 epochs for the step one and for 25 epochs for the step two.
For models using the center loss a centroid learning rate of 0.001 is used.
The other hyperparameters are analyzed performing an ablation on appendix \ref{sec:tables}.

@@

\subsection{Results}
\label{sec:results}
\begin{figure}[!htb]
  \centering
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a1.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-a2.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-l.png}
  \end{subfigure}
  \begin{subfigure}[!htb]{0.35\textwidth}
    \includegraphics[trim=0 0 0 2cm, clip, width=\linewidth]{hos-th.png}
  \end{subfigure}
  \caption{\centering\label{figurelabel} HOS values for different parameters. For full reference see appendix \ref{sec:tables}}
\end{figure}

@@

The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
A few critical points still remain on our method of study and proposed solution.
The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.

\newpage
\appendix
\section{Tables}
\label{sec:tables}

This section contains tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report the hyperparameters optimization sequence, while tables \ref{tab:results} report the final values for each domain shift with the chosen hyperparameters.

@@

\begin{table*}
  \centering
  \begin{tabular}[t]{||c||c|c|c|c||c|c|c|c||c|c|c|c||}
    \hline
    \multicolumn{13}{||c||}{Results} \\
    \hline
    \multirow{2}{*}{Shift}   & \multicolumn{4}{|c||}{Single-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, Center Loss} \\
            & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   \\
    \hline
    A$\to$C & 52.07 & 44.76 & 58.65 & 36.19 & 57.46 & 46.64 & 62.95 & 37.04 & 59.77 & 52.68 & 62.73 & 45.40 \\
    A$\to$P & 50.84 & 51.27 & 57.56 & 46.23 & 56.31 & 54.13 & 60.42 & 49.03 & 56.86 & 52.46 & 63.35 & 44.77 \\
    A$\to$R & ??.?? & ??.?? & ??.?? & ??.?? & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
    C$\to$A & 49.52 & 41.74 & 43.10 & 40.47 & 55.28 & 42.63 & 51.57 & 36.33 & 55.76 & 46.84 & 60.19 & 38.35 \\
    C$\to$P & 54.42 & 46.99 & 41.51 & 54.15 & 59.13 & 51.88 & 60.03 & 45.69 & 58.35 & 52.69 & 62.19 & 45.72 \\
    C$\to$R & 53.43 & 46.18 & 38.64 & 57.39 & 60.75 & 56.00 & 61.29 & 51.63 & 59.15 & 55.97 & 63.18 & 50.25 \\
    P$\to$A & 48.32 & 37.07 & 33.70 & 41.20 & 55.62 & 41.72 & 48.90 & 36.39 & 53.50 & 40.97 & 49.53 & 34.94 \\
    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & ??.?? & ??.?? & ??.?? & ??.?? \\
    P$\to$R & 50.37 & 34.14 & 22.88 & 67.27 & 59.68 & 48.41 & 40.91 & 59.30 & 61.10 & 56.22 & 56.89 & 55.58 \\
    R$\to$A & 49.39 & 25.08 & 15.99 & 58.19 & 58.47 & 45.00 & 39.50 & 52.43 & 57.98 & 48.92 & 45.61 & 52.77 \\
    R$\to$C & 49.80 & 46.70 & 48.27 & 45.23 & 57.02 & 49.00 & 42.82 & 57.34 & 57.09 & 48.69 & 61.11 & 40.47 \\
    R$\to$P & 54.10 & 23.37 & 13.89 & 73.69 & 62.33 & 50.31 & 39.51 & 69.27 & 63.96 & 59.64 & 54.40 & 66.02 \\
    \hline
    AVG     & ??.?? & ??.?? & ??.?? & ??.?? & 52.23 & 49.03 & 51.35 & 49.56 & ??.?? & ??.?? & ??.?? & ??.?? \\ 
    \hline
  \end{tabular}
  \caption{\centering\label{tab:results}Results for each configuration and each domain shift. All values are percentages.}
\end{table*}
